\documentclass{article}
\title{On Autonomous vehicles - Systems and Algorithms}
\author{.}


\begin{document}
\maketitle
\section{Simultaneous Localization And Mapping(SLAM) }
Estimating the vehicle position and surrounding map  is a necessary condition to achieve autonomous driving. There are multiple sensors like LIDAR, RADAR, Inertial Measurement Unit(IMU), GPS and the stereo Camera are  used to obtain a surrounding map. A navigational map  is obtained by fusing the data from these  sensors.\\

\subsection{Generic Methods}
Following are the commonly used sensor fusion algorithms used in SLAM.\\

\begin{tabular}{|p{3cm}|p{2cm}|p{3cm}|p{4cm}|}
\hline
Algorithm	&Algorithm Type	&Computational Effort	&Theoritical base\\
\hline
Histogram Filters	&SLAM	&High	&Bayes\\
\hline
Particle Filters\cite{pf}	&SLAM 	&Medium	&Bayesian recursion\\
\hline
Extended Kalman filters\cite{ekf}	&SLAM	&Medium	&Kalman Filters\\
\hline
Rao-Blackwellised Filter\cite{rb}	&SLAM	&Minimum	&Reduce the sample-space by applying Rao-Blackwellisation (R-B)\\
\hline
Bundle adjustment	&Visual SLAM	&High	&predicted projection of points\\
\hline
\end{tabular}

\subsection{Visual SLAM(VSLAM)}
Instead of using high cost sensors such as LIDAR, VSLAM techniques uses camera as the basic sensor.
Following are the commonly used sensor fusion algorithms used in SLAM.\\
\begin{tabular}{|p{3cm}|p{2cm}|p{3cm}|p{4cm}|}
\hline
Algorithm	&Algorithm Type	&Computational Effort	&Theoritical base\\
\hline
Multi-frame Feature Integration\cite{mfi}	&Visual Odometry	&High	&Optical flow\\
\hline
TLBBA\cite{tlbba}	&Visual Odometry	&High	&Stereo odometry\\
\hline
2FO-CC	&Visual Odometry	&High	&Correcting the Calibration Bias\\
\hline
VOFSLBA	&Visual Odometry\cite{flow}	&High	&flow separation and local bundle adjustment\\
\hline
\end{tabular}


\section{Motion Planning}

Map obtained from a SLAM algorithm is used to plan the motion of the vehicle through the given GPS waypoints. Some of the algorithms used to  plan the motion of an autonomous vehicle is given below.\\


\begin{tabular}{|p{3cm}|p{2cm}|p{3cm}|p{3cm}|}
\hline
Algorithm	&Algorithm Type	&Computational Effort	&Theoritical base\\
\hline
A* \cite{a}	&Search	&High	& Edsger Dijkstra's 1959 algorithm\\
\hline
D*\cite{d}	& Search	&High	& incremental search algorithm\\
\hline
Anytime Dynamic A*\cite{aa}	&Search	&High	&A*\\
\hline
 Probabilistic roadmap\cite{p}	&Search	&High	&Random sampling\\
\hline

\end{tabular}





\section{Object detection, recognition and scene understanding}
Object recognition algorithms are used to understand the objects/obstacles  around the vehicle. The primary obstacle avoidance methods are based on the point clouds generated from the LIDAR and RADAR data.  But the object recognition methods are more rely on the visual sensors such as camera. Majority of the algorithms uses supervised  machine learning methods to recognize the object. Some of the widely used methods are listed below.\\

\begin{tabular}{|p{3cm}|p{2cm}|p{3cm}|p{3cm}|}
\hline
Algorithm	&Algorithm Type	&Computational Effort	&Theoritical base\\
\hline
Bayesian Classification\cite{bc}	&Classification	&High	&Bayes\\
\hline
Deep Convolutional network\cite{dc}	&Classification	&High	&neural networks\\
\hline
Support Vector Machine\cite{svm}	&Classification	&High	&Kernel Tricks\\
\hline

\end{tabular}





\begin{thebibliography}{9}
\bibitem{ekf}
Julier, Simon J., and Jeffrey K. Uhlmann. "Unscented filtering and nonlinear estimation." Proceedings of the IEEE 92.3 (2004): 401-422.
\bibitem{pf}Pitt, Michael K., and Neil Shephard. "Filtering via simulation: Auxiliary particle filters." Journal of the American statistical association 94.446 (1999): 590-599.
\bibitem{rb}Grisetti, Giorgio, Cyrill Stachniss, and Wolfram Burgard. "Improved techniques for grid mapping with rao-blackwellized particle filters." Robotics, IEEE Transactions on 23.1 (2007): 34-46.
\bibitem{mfi}Badino, Hernán, Akihiro Yamamoto, and Takeo Kanade. "Visual odometry by multi-frame feature integration." Computer Vision Workshops (ICCVW), 2013 IEEE International Conference on. IEEE, 2013.
\bibitem{tlbba}Lu, Wei, Zhiyu Xiang, and Jilin Liu. "High-performance visual odometry with two-stage local binocular ba and gpu." Intelligent Vehicles Symposium (IV), 2013 IEEE. IEEE, 2013.
\bibitem{flow}Kaess, Michael, Kai Ni, and Frank Dellaert. "Flow separation for fast and robust stereo odometry." Robotics and Automation, 2009. ICRA'09. IEEE International Conference on. IEEE, 2009.
\bibitem{a}Delling, Daniel, et al. "Engineering route planning algorithms." Algorithmics of large and complex networks. Springer Berlin Heidelberg, 2009. 117-139.
\bibitem{d}Stentz, Anthony. "The focussed D\^* algorithm for real-time replanning." IJCAI. Vol. 95. 1995.

\bibitem{p}Boor, Valérie, Mark H. Overmars, and A. Frank van der Stappen. "The Gaussian sampling strategy for probabilistic roadmap planners." Robotics and automation, 1999. proceedings. 1999 ieee international conference on. Vol. 2. IEEE, 1999.
\bibitem{aa}Likhachev, Maxim, et al. "Anytime Dynamic A*: An Anytime, Replanning Algorithm." ICAPS. 2005.
\bibitem{bc}Williams, Christopher KI, and David Barber. "Bayesian classification with Gaussian processes." Pattern Analysis and Machine Intelligence, IEEE Transactions on 20.12 (1998): 1342-1351.
\bibitem{dc}Krizhevsky, Alex, Ilya Sutskever, and Geoffrey E. Hinton. "Imagenet classification with deep convolutional neural networks." Advances in neural information processing systems. 2012.
\bibitem{svm}Suykens, Johan AK, and Joos Vandewalle. "Least squares support vector machine classifiers." Neural processing letters 9.3 (1999): 293-300.

\end{thebibliography}
\end{document}


